\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Now that this general framework explained, we can add some heuristics based on neuro-scientific observations to constrain our model and its strategies to solve the task  used to solve the ecological task described in section~\ref{sec:task}. Note that the general framework is the same as the one presented in~\cite{grimaldi_learning_2022} and that, apart from the more complex task to solve and a deeper analysis of the results, these novel heuristics, inspired by neuroscience, are the main methodological differences with that previous study. In our simulations, We set the size of the kernels to $(21, 17, 17)$ and define as many classes as the number of motions (directions and speeds): $N_\class = 8 \times 3$. To avoid introducing biases in the directions, we apply a circular mask on the spatial dimensions of the kernels. First, we observed that moving images produced trajectories of ON and OFF spikes, and that these were present in both arrangements of polarities. This is due to the fact that our whitened images show a symmetry in the luminance profiles, and that an image with inverted contrast is indistinguishable. As this arrangement of polarities is independent of the speed, we added a mechanism gathering the linear values for the movie and the movie with ON and OFF cells flipped, and kept only the maximal value for each voxel. This is similar to the computation operated for complex cells in the primary visual cortex.  Second, we included a prior in the motions that could be selected, as there is a prior in natural scenes for slow speeds~\citep{vacher_bayesian_2018}. As here we aim at capturing the possible convergence of events' trajectories converging to each voxel, we thus apply a mask on the spatio-temporal kernels such that the connectivity is bounded by the delay: the lower the delay, the lower the circular mask radius (\seeFig{kernels} for an illustration). This is compatible with neuroscientific principles because of the limits in conduction delay along horizontal connections, the synaptic delay is linked, by physical principles, to the distance between the presynaptic neuron and the postsynaptic one.

>>>>

Now that this general framework has been explained, we can add some heuristics, based on neuroscientific observations, to constrain our model and its strategies for solving the task that is used to solve the ecological task described in section~\ref{sec:task}. Note that the general framework is similar to that presented in~\cite{grimaldi_learning_2022} and that, apart from the more complex task to solve and a deeper analysis of the results, these novel heuristics inspired by neuroscience are the main methodological differences with that previous study. In our simulations, we set the size of the kernels to $(21, 17, 17)$ and define as many classes as the number of motions (directions and velocities): $N_\class = 8 \times 3$. To avoid introducing biases in the directions, we apply a circular mask to the spatial dimensions of the kernels. First, we observed that moving images produced trajectories of ON and OFF spikes, and that these were present in both polarities arrangements. This is due to the fact that our whitened images have a symmetry in the luminance profiles, and an image with inverted contrast is indistinguishable. Since this arrangement of polarities is independent of speed, we added a mechanism that collects the linear values for the movie and the movie with the ON and OFF cells flipped, keeping only the maximum value for each voxel. This is similar to the computation done for complex cells in primary visual cortex.  Second, we included a prior in the motions that could be selected, as there is a prior in natural scenes for slow speeds~\citep{vacher_bayesian_2018}. Since we want to capture the possible convergence of the trajectories of the events converging on each voxel, we apply a mask to the spatiotemporal kernels so that the connectivity is limited by the delay: the smaller the delay, the smaller the radius of the circular mask that is applied (\seeFig{kernels} for an illustration). This is consistent with neuroscientific principles because, due to the limits of the conduction delay along horizontal connections, the synaptic delay is related, by physical principles, to the distance between the presynaptic neuron and the postsynaptic one.
